Bootstrapping Multi-atlas Segmentation Using Multiple Automatically Generated Templates for the Segmentation of the Whole Hippocampus and Subfields

### 2013-12-22 paper.Rnw
Figure comments, WA validation schematic update, various fixes

% shortcuts 
\newcommand{\mb}{MAGeT-Brain}
\newcommand{\multiatlas}{multi-atlas}
\newcommand{\ants}{ANTS}
\newcommand{\animal}{ANIMAL}
\newcommand{\adnidataset}{ADNI1:Complete 1Yr 1.5T}
\newcommand{\FEPdataset}{SZ-FEP}
\newcommand{\fsl}{FSL}
\newcommand{\freesurfer}{FreeSurfer}
\newcommand{\maper}{MAPER}
\newcommand{\gs}{Gold Standard}
\newcommand{\silver}{silver standard}
\newcommand{\prsnr}{Pruessner}
\newcommand{\pseg}{\prsnr-protocol manual segmentation}
\newcommand{\psegs}{\prsnr-protocol manual segmentations}
\newcommand{\snt}{SNT}

@@

\textbf{Introduction:} 
Advances in image segmentation of magnetic resonance images (MRI) have
demonstrated that \multiatlas{} approaches improve segmentation accuracy and
precision over regular atlas-based approaches.  These approaches often rely on
a large number of such manually segmented atlases (e.g.  30-80) that take
significant time and expertise to produce. We present an algorithm, \mb{} 
({\textbf M}ultiple {\textbf A}utomatically {\textbf Ge}nerated {\textbf
T}emplates), for the automatic segmentation of the hippocampus that minimizes
the number of atlases needed while still achieving similar accuracy to
\multiatlas{} approaches. Thus, our method acts as an accurate \multiatlas{}
approach when using special, hard-to-define atlases that are laborious to
construct. \\
\textbf{Method:} \mb{} works by propagating atlas segmentations to a template
library, formed from a subset of target images, via transformations estimated by
non-linear image registration. The resultant segmentations are then propagated
to each target image and fused using a label fusion method.  To explore the
effect of atlases and templates library size, registation and label
fusion method, we conduct a 10-fold Monte Carlo cross-validation of \mb{} of whole
hippocampal segmentation on 60 ADNI subjects, manually segmented using the
\prsnr{}-protocol, over a range of parameter settings. Using the best settings
found, we then conduct a leave-one-out cross-validation (LOOCV) of hippocampal
subfield segmentation using five high-resolution manually segmented atlases.
Two final experiments assess \mb{} when applied to first episode psychosis and
Alzheimer's disease populations, and \mb{} segmentations are compared with
existing automated methods (\fsl{}, \freesurfer{}, \maper{}) and biases are
explored.\\
\textbf{Results:} Using nine atlases and 19 template images, \mb{} achieves a
mean Dice's Similarity Coefficient (DSC) of 0.88 (to \psegs{}) over 10-folds of
Monte Carlo % TODO: update cross-validation on 60 subjects, and shows
significantly lower variability in DSC than \multiatlas{} segmentation.
In a LOOCV, \mb{} reproduces the volumes of the cornu ammonis (CA) 1;
CA4/dentate % TODO: update
gyrus (DG); and strata radiatum (SR), strata lacunosum (SL), and strata
moleculare (SM) hippocampal subfields with a percent error in volume that is
at or lower than that produced by image resampling. \mb{} produces hippocampal
volumes in a first episode psychosis patient population that are highly
correlated with expert manual segmentation volumes (Pearson $r = 0.877, t =
16.244, p < 0.001$). Compared to \fsl{} and \freesurfer{}, \mb{} shows much smaller
fixed volume bias (within $250 mm^3$ on average) to semi-automated (\snt{})
segmentations available from ADNI, as well as a conservative, rather than
exaggerated, proportional volume bias.\\ \textbf{Conclusion:} We demonstrate
that \mb{} produces accurate hippocampal segmentations using only 5 atlases over
different hippocampal definitions, disease populations, and acquisition types,
as well as showing that accurate identification of the hippocampal subfields is
possible.
\end{abstract}

@@

\begin{figure}
  \begin{centering}
    \includegraphics[width=\textwidth]{figure/MA-MAGeTBrain-Schematic}
  \end{centering}
  \caption{A schematic illustration of basic \multiatlas{} segmentation and \mb{}
  segmentation \label{fig:MAGeT}}
\end{figure}

@@

where $A$ and $B$ are the regions being compared, and the cardinality is the
volume measured in voxels.

The labels produced by \mb{} and \multiatlas{} segmentation are compared to the
manual labels using the Dice similarity coefficient, and the recorded value for
each subject at each parameter setting explored in this experiment is the
average over ten validation rounds.

@@

Specifically, two sets of $0.9mm^3$ voxel target images are used in this
experiment: separately acquired T1 acquisitions of four of the five Winterburn
atlas subjects (referred to as the {\em BRAVO} set because of the scan
parameters used, described below), and computationally subsampled versions of
the Winterburn atlas images (the {\em Subsampled} set).

@@

Image subsampling of the Winterburn atlases was performed using trilinear
interpolation techniques.

The template library is composed of all $0.9mm^3$ voxel target images
(either {\em BRAVO} or {\em Subsampled}), plus an additional set of 16 of
healthy subjects 3T T1 images acquired separately (Table
\ref{tab:WAval-healthy-demographics}). These images were acquired on a 3T GE
Discovery MR 750 system (General Electric, Milwaukee, WI) using an 8-channel
head coil with the enhanced fast gradient recalled echo 3-dimensional
acquisition protocol, EFGRE-BRAVO, with the following parameters: $TE/TR/TI =
3.0ms/6.7ms/650ms$, flip angle=$8^\circ$ , $FOV = 15.3cm$, slice
thickness$=0.9mm$, 170 in-plane steps for an approximate isotropic resolution of
0.9mm dimension voxels.

@@

\begin{figure}
  \begin{centering}
    \includegraphics[width=\textwidth]{figure/WinterburnSubfieldLOOCVSchematic}
  \end{centering}
  \caption{A schematic illustration of the experimental set up of the
  leave-one-out cross-validation (LOOCV) subfield experiment.}
  \label{fig:LOOCV-schematic}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Subfield Validation Template library demographics (healthy controls)
%                                     
<<WAval-healthy-demographics, echo=F, results="asis",cache=FALSE>>=
master = read.csv('data/DT_study.csv')
tab <- summary( Diagnosis ~ Age + Sex + Education + Handedness, data = master,
    method="reverse", na.rm = TRUE, test=FALSE)
caption = 
  "\\textbf{Demographics for the hippocampal subfield cross-validation healthy
control subject sample.} Education is shown in years."
latex(tab, file="", size="scriptsize",landscape=FALSE, ctable=FALSE,
      caption=caption, caption.loc = c("top"),
      title="tab:WAval-healthy-demographics")
@
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Evaluation method}  
In this experiment we must evaluate \mb{} on a task which is ill-defined since
there are no segmentation protocols of the hippocampal subfields for T1 images
at $0.9mm^3$ voxels (in fact, whether subfields can even be differentiated at
this resolution is debated \citep{who?}). Therefore, we evaluate the {\it
precision} with \mb{} produces hippocampal subfields that correspond to the
segmentation protocol used by the given atlas library images.

Specifically, we compute the relative percent error in volume of the \mb{}-produced
hippocampal subfields with respect to the full-resolution Winterburn atlas
segmentations. In addtion, by directly resampling the Winterburn atlas
segmentations to $0.9mm^3$ voxel images (using nearest-neighbour interpolation)
we can obtain a baseline relative percent error to compare \mb{} against.

@@

One author (MP) performed visual quality inspection for \mb{} and \freesurfer{} 
segmentations using similar quality control guidelines (if either hippocampus
was under or over segmented by $10mm$ or greater in three or more slices then
the segmentation did not pass).  Only images meeting the conditions of having
segmentations from all methods (\snt{}, \maper{}, \freesurfer{}, \fsl{}, and \mb{}) and also
passing quality control inspection were included in the analysis.

@@

In addition to an improvement in accuracy over \multiatlas{}-based segmentation,
\mb{} also shows a decrease in the variability of segmentation accuracy 
(Figure \ref{ADNI1-xval-variability}).  The size of template library 
necessary to reach a decrease ($p < 0.05$) in variance and standard deviation
grows with the size of atlas library used.  A template library of 19 images is
sufficient to show significant decrease in variance and standard deviation for
3-7 atlases.

@@

\begin{sidewaysfigure}
    \begin{centering}
      \includegraphics[width=\linewidth]{figure/winterburn-atlas-montage/figure.pdf}
    \end{centering}
    \caption{Detailed subfield segmentation results for a single subject. In
    the upper left corner is the original high-resolution Winterburn atlas manual
    subfield segmentation; in the upper right corner is the Winterburn atlas
    segmentation resampled from 0.3mm- to 0.9mm-isotropic voxels; in the lower left
    corner is the \mb{} segmentation of the resampled Winterburn atlas images; in the
    lower right corner is the \mb{} segmentation of a separately acquired T1 BRAVO
    image of the same subject. In each segmentation, slices from the left
    hemisphere are shown in Talairach-like ICBM152 space: the first row shows axial
    slices from inferior to superior; the second row shows sagittal slices from
    lateral to medial; the third row shows coronal slices from anterior to
    posterior.  \label{fig:subfield-montage}}
\end{sidewaysfigure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tabulation of segmentation accuracies of existing methods (ADNI)
%
%
\begin{table}[!tbp]
\scriptsize
\caption{\textbf{Automated segmentation accuracy (overlap with \snt{} labels)
of the ADNI dataset.} For each method, the number of labelled atlases
used for training, the best Dice's overlap measure, the disease classes
measured, and the validation procedure are shown. Unless specified, validation
datasets are composed equally of subjects diagnosed with Alzheimer's Disease
(AD), Mild Cognitive Impairment (MCI), and Cognitively Normal (CN). LOOCV =
Leave-one-out cross-validation. 
   Some studies of automated segmentation of ADNI images are excluded because they 
   do not not provide overlap measures for the hippocampus \citep{Heckemann2011,Chupin2009}.
  \label{tab:other-methods}} 
\begin{center}
\begin{tabular}{ l  c  p{1in}  l  p{2in}  }
\hline\hline
Method & Atlases & DSC & Reference & Validation \tabularnewline
\hline
\mb{}                     &9 & \Sexpr{round(mb.best.kappa, digits=3)} & & 10
rounds of Monte Carlo CV on a pool of 69 subjects \tabularnewline % TODO: update
LEAP                    &30&0.848                 &\cite{Wolz2010}  &Segmentation of 60 subjects\tabularnewline
ACM (AdaBoost-based)    &21&0.862                 &\cite{Morra2008} &LOOCV on atlases\tabularnewline
Patch-based label fusion&16&0.883 (CN) \newline 0.838 (AD)&\cite{Coupe2011e}&LOOCV on atlases\tabularnewline
Multi-atlas             &30&0.885                 &\cite{Lotjonen2010}&Segmentation of 60 subjects\tabularnewline
Multi-atlas + weighted fusion&20&0.898 (CN) \newline 0.798 (left HC, MCI) &\cite{Wang2011}  &10 rounds of Monte Carlo CV on 20 subjects, pool of 139 (CN/MCI)\tabularnewline
Multi-atlas (MAPS)    &55&0.890                   &\cite{Leung2010}&Segmentation of 30 subjects (10 AD, MCI, and CN)\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: prep
% Prepares the data in a the form needed for plotting.
<<ADNI1-SNT-xval-prep,dependson='ADNI1-xval-load',include=FALSE,cache=TRUE>>=
snt_xval_data  <- read.csv(gzfile('data/cache/ADNI-SNT-XVAL:all_data.csv.gz'))
snt_xval_mean  <- read.csv(gzfile('data/cache/ADNI-SNT-XVAL:all_data_mean.csv.gz'))

>>>>

% shortcuts 
\newcommand{\mb}{MAGeT-Brain}
\newcommand{\multiatlas}{multi-atlas}
\newcommand{\ants}{ANTS}
\newcommand{\animal}{ANIMAL}
\newcommand{\adnidataset}{ADNI1:Complete 1Yr 1.5T}
\newcommand{\FEPdataset}{SZ-FEP}
\newcommand{\fsl}{FSL FIRST}
\newcommand{\freesurfer}{FreeSurfer}
\newcommand{\maper}{MAPER}
\newcommand{\gs}{Gold Standard}
\newcommand{\silver}{silver standard}
\newcommand{\prsnr}{Pruessner}
\newcommand{\pseg}{\prsnr-protocol manual segmentation}
\newcommand{\psegs}{\prsnr-protocol manual segmentations}
\newcommand{\snt}{SNT}

@@

\textbf{Introduction:} 
Advances in image segmentation of magnetic resonance images (MRI) have
demonstrated that \multiatlas{} approaches improve segmentation accuracy and
precision over regular atlas-based approaches.  These approaches often rely on
a large number of such manually segmented atlases (e.g.  30-80) that take
significant time and expertise to produce. We present an algorithm, \mb{} 
({\textbf M}ultiple {\textbf A}utomatically {\textbf Ge}nerated {\textbf
T}emplates), for the automatic segmentation of the hippocampus that minimizes
the number of atlases needed while still achieving similar accuracy to
\multiatlas{} approaches. Thus, our method acts as an accurate \multiatlas{}
approach when using special, hard-to-define atlases that are laborious to
construct. \\
\textbf{Method:} \mb{} works by propagating atlas segmentations to a template
library, formed from a subset of target images, via transformations estimated by
non-linear image registration. The resultant segmentations are then propagated
to each target image and fused using a label fusion method.  To explore the
effect of atlases and templates library size, registation and label
fusion method, we conduct a 10-fold Monte Carlo cross-validation of \mb{} of whole
hippocampal segmentation on 60 ADNI subjects, manually segmented using the
\prsnr{}-protocol, over a range of parameter settings. Using the best settings
found, we then conduct a leave-one-out cross-validation (LOOCV) of hippocampal
subfield segmentation using five high-resolution manually segmented atlases.
Two final experiments assess \mb{} when applied to first episode psychosis and
Alzheimer's disease populations, and \mb{} segmentations are compared with
existing automated methods (\fsl{}, \freesurfer{}, \maper{}) and biases are
explored.\\
\textbf{Results:} Using 9 atlases and 19 template images, \mb{} achieves a
mean Dice's Similarity Coefficient (DSC) of \Sexpr{round(mb.best.kappa, digits=3)} 
(to \psegs{}) over 10-folds of Monte Carlo % TODO: update cross-validation on 60 subjects, and shows
significantly lower variability in DSC than \multiatlas{} segmentation.
In a LOOCV, \mb{} reproduces the volumes of the cornu ammonis (CA) 1;
CA4/dentate % TODO: update
gyrus (DG); and strata radiatum (SR), strata lacunosum (SL), and strata
moleculare (SM) hippocampal subfields with a percent error in volume that is
at or lower than that produced by image resampling. \mb{} produces hippocampal
volumes in a first episode psychosis patient population that are highly
correlated with expert manual segmentation volumes (Pearson $r = 0.877, t =
16.244, p < 0.001$). Compared to \fsl{} and \freesurfer{}, \mb{} shows much smaller
fixed volume bias (within $250 mm^3$ on average) to semi-automated (\snt{})
segmentations available from ADNI, as well as a conservative, rather than
exaggerated, proportional volume bias.\\ \textbf{Conclusion:} We demonstrate
that \mb{} produces accurate hippocampal segmentations using only 5 atlases over
different hippocampal definitions, disease populations, and acquisition types,
as well as showing that accurate identification of the hippocampal subfields is
possible.
\end{abstract}

@@

\begin{figure}
  \begin{centering}
    \includegraphics[width=\textwidth]{figure/MA-MAGeTBrain-Schematic}
  \end{centering}
  \caption{A schematic illustration of basic \multiatlas{} segmentation and
\mb{} segmentation. In multi-atlas segmentation, manual labels from atlas images
are warped (propagated) into subject space by applying the transformations
estimated from non-linear image registration. The resulting candidate labels
from all atlas images are then fused to create a final segmentation. In \mb{}
segmentation, a template library is created by sampling (either randomly or
representatively) from the subject images. Atlas labels are propagated to all
template images and then to each subject image (including those used in the template
library). The candidate the labels for a subject are then fused into a final
segmentation.  \label{fig:MAGeT}}
\end{figure}

@@

where $A$ and $B$ are the regions being compared, and the cardinality is the
volume measured in voxels. The labels produced by \mb{} and \multiatlas{}
segmentation are compared to the manual labels using the Dice similarity
coefficient, and the recorded value for each subject at each parameter setting
explored in this experiment is the average over ten validation rounds.

@@

Specifically, this experiments has two parts, each using different sets of
$0.9mm^3$ voxel target images: trilinear subsampled versions of the Winterburn
atlas images (Experiment 2a), and separately acquired T1 BRAVO acquisitions of
four of the five Winterburn atlas subjects (Experiment 2b).  Image subsampling
of the Winterburn atlas images was performed using trilinear subsampling
techniques.

@@

The template library is composed of all $0.9mm^3$ voxel target images (either
the {\em BRAVO} or {\em subsampled} sets), plus an additional set of 16 of
healthy subjects 3T T1 images acquired separately (Table
\ref{tab:WAval-healthy-demographics}). These images were acquired on a 3T GE
Discovery MR 750 system (General Electric, Milwaukee, WI) using an 8-channel
head coil with the enhanced fast gradient recalled echo 3-dimensional
acquisition protocol, EFGRE-BRAVO, with the following parameters: $TE/TR/TI =
3.0ms/6.7ms/650ms$, flip angle=$8^\circ$ , $FOV = 15.3cm$, slice
thickness$=0.9mm$, 170 in-plane steps for an approximate isotropic resolution of
0.9mm dimension voxels.

@@

\begin{figure}
  \begin{centering}
    % TODO: fix schematic
    \includegraphics[width=\textwidth]{figure/WinterburnSubfieldLOOCVSchematic}
  \end{centering}
  \caption{A schematic illustration of the experimental set up of the
  leave-one-out cross-validation (LOOCV) subfield experiment.}
  \label{fig:LOOCV-schematic}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Subfield Validation Template library demographics (healthy controls)
%                                     
<<WAval-healthy-demographics, echo=F, results="asis",cache=FALSE>>=
master = read.csv('data/DT_study.csv')
tab <- summary( Diagnosis ~ Age + Sex + Education + Handedness, data = master,
    method="reverse", na.rm = TRUE, test=FALSE)
caption = 
  "\\textbf{Demographics for the hippocampal subfield cross-validation healthy
control subject sample used in the template library (excluding the Winterburn
atlas subjects).} Education is shown in years."
latex(tab, file="", size="scriptsize",landscape=FALSE, ctable=FALSE,
      caption=caption, caption.loc = c("top"),
      title="tab:WAval-healthy-demographics")
@
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Evaluation method}  
Evaluating the accuracy of hippocampal subfields for T1 images at
$0.9mm^3$-isotropic voxels is inherently ill-defined since there are no manual
protocols for segmentation at this resolution to use as a reference. Instead, we
can evaluate the {\it precision} with which \mb{} produces hippocampal subfields
that correspond to the segmentation protocol used by the given atlas library
images.  Specifically, we compute the relative percent error in volume of the
\mb{}-produced hippocampal subfields with respect to the full-resolution
Winterburn atlas segmentations. In addtion, by directly resampling the
Winterburn atlas segmentations to $0.9mm^3$ voxels (using standard
nearest-neighbour image resampling techniques) we obtain a scaled down version
of the labels preserving the original segmentation protocol within the limits of
error from rounding and interpolation. The relative percent error in volume of
these labels provides a baseline to compare \mb{} segmentations against.

@@

One author (MP) performed visual quality inspection for \mb{} and \fsl{} 
segmentations using similar quality control guidelines (if either hippocampus
was under or over segmented by $10mm$ or greater in three or more slices then
the segmentation did not pass).  Only images meeting the conditions of having
segmentations from all methods (\snt{}, \maper{}, \freesurfer{}, \fsl{}, and \mb{}) and also
passing quality control inspection were included in the analysis.

@@

In addition to an improvement in accuracy over \multiatlas{}-based segmentation,
\mb{} also shows a decrease in the variability of segmentation accuracy 
(Figure \ref{fig:ADNI1-xval-variability}).  The size of template library 
necessary to reach a decrease ($p < 0.05$) in variance and standard deviation
grows with the size of atlas library used.  A template library of 19 images is
sufficient to show significant decrease in variance and standard deviation for
1-9 atlases.

@@

\begin{sidewaysfigure}
    \begin{centering}
      \includegraphics[width=\linewidth]{figure/winterburn-atlas-montage/figure.pdf}
    \end{centering}
    \caption{Detailed subfield segmentation results for a single subject. In
    the upper left corner is the original high-resolution Winterburn atlas manual
    subfield segmentation; in the upper right corner is the Winterburn atlas
    segmentation subsampled from 0.3mm- to 0.9mm-isotropic voxels; in the lower left
    corner is the \mb{} segmentation of the subsampled Winterburn atlas images; in the
    lower right corner is the \mb{} segmentation of a separately acquired T1 BRAVO
    image of the same subject. In each segmentation, slices from the left
    hemisphere are shown in Talairach-like ICBM152 space: the first row shows axial
    slices from inferior to superior; the second row shows sagittal slices from
    lateral to medial; the third row shows coronal slices from anterior to
    posterior.  \label{fig:subfield-montage}}
\end{sidewaysfigure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tabulation of segmentation accuracies of existing methods (ADNI)
%
%
\begin{table}[!tbp]
\scriptsize
\caption{\textbf{Automated segmentation accuracy (overlap with \snt{} labels)
of the ADNI dataset.} For each method, the number of labelled atlases
used for training, the best Dice's overlap measure, the disease classes
measured, and the validation procedure are shown. Unless specified, validation
datasets are composed equally of subjects diagnosed with Alzheimer's Disease
(AD), Mild Cognitive Impairment (MCI), and Cognitively Normal (CN). LOOCV =
Leave-one-out cross-validation. 
   Some studies of automated segmentation of ADNI images are excluded because they 
   do not not provide overlap measures for the hippocampus \citep{Heckemann2011,Chupin2009}.
  \label{tab:other-methods}} 
\begin{center}
\begin{tabular}{ l  c  p{1in}  l  p{2in}  }
\hline\hline
Method & Atlases & DSC & Reference & Validation \tabularnewline
\hline
LEAP                    &30&0.848                 &\cite{Wolz2010}  &Segmentation of 60 subjects\tabularnewline
ACM (AdaBoost-based)    &21&0.862                 &\cite{Morra2008} &LOOCV on atlases\tabularnewline
\mb{}                   &9 & \Sexpr{round(mb.best.kappa, digits=3)} & & 10
rounds of Monte Carlo CV on a pool of 69 subjects \tabularnewline % TODO: update
Patch-based label fusion&16&0.883 (CN) \newline 0.838 (AD)&\cite{Coupe2011e}&LOOCV on atlases\tabularnewline
Multi-atlas             &30&0.885                 &\cite{Lotjonen2010}&Segmentation of 60 subjects\tabularnewline
Multi-atlas + weighted fusion&20&0.898 (CN) \newline 0.798 (left HC, MCI) &\cite{Wang2011}  &10 rounds of Monte Carlo CV on 20 subjects, pool of 139 (CN/MCI)\tabularnewline
Multi-atlas (MAPS)    &55&0.890                   &\cite{Leung2010}&Segmentation of 30 subjects (10 AD, MCI, and CN)\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: prep
% Prepares the data in a the form needed for plotting.
<<ADNI1-SNT-xval-prep,include=FALSE,cache=TRUE>>=
snt_xval_data  <- read.csv(gzfile('data/cache/ADNI-SNT-XVAL:all_data.csv.gz'))
snt_xval_mean  <- read.csv(gzfile('data/cache/ADNI-SNT-XVAL:all_data_mean.csv.gz'))
snt_xval_mean$reg_method = factor(snt_xval_mean$reg_method, c("ANTS", "ANIMAL"))
snt_xval_mean$method.mb = factor(snt_xval_mean$method.mb, c("Majority Vote", "Cross-correlation Vote", "NMI Vote"))
